### 2017-08-17 Paper01_EnthalpyAndCrystallization.tex
Sub - added sub image of annealing xrd normalised.

@@

>>>>

The bulk is shown in Figure \ref{fig:XRD_Dynamic_Bulk}, and film in Figure \ref{fig:XRD_Dynamic_Film}.

@@

%single image
\begin{figure}[b]
	\centering
	\includegraphics[width=0.85\textwidth]{XRD_Normalised_Annealing_BulkFilm_Facet.png}
	\caption{Supplementary: Annealing \acrshort{xrd} pattern for both bulk and film \MgZnCa~ heated treated to several temperatures for crystallisation peak identified from \acrshort{dsc}. Note the patterned have been normalised and the Al substrate peaks have been faceted as to not dwarf all other peaks.}
	\label{fig:XRD_Annealing_BulkandFilm}
\end{figure}
